Automated segmentation and description of the internal morphology of human permanent teeth by means of micro-CT

### 2021-03-10 manuscript.tex
Merge branch 'master' of github.com:habi/zmk-tooth-cohort-method-manuscript [ci skip]
This build is based on
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/478f12f982a0804c2c55f1074f2c468764dad512.

This commit was created by the following CI build and job:
https://github.com/habi/zmk-tooth-cohort-method-manuscript/commit/478f12f982a0804c2c55f1074f2c468764dad512/checks
https://github.com/habi/zmk-tooth-cohort-method-manuscript/runs/639946944

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...544c934c122c7dc4c17a91fa0ac65fd48d5d80ea}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/544c934c122c7dc4c17a91fa0ac65fd48d5d80ea/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/544c934c122c7dc4c17a91fa0ac65fd48d5d80ea}{habi/zmk-tooth-cohort-method-manuscript@544c934}
on March 9, 2021.

@@

\leavevmode\hypertarget{ref-10OKzEtEb}{}%
37. Fedlex. \url{https://www.fedlex.admin.ch/eli/cc/2013/617/en}. Accessed 9 Mar 2021.
\end{cslreferences}

>>>>

A preprint of this manuscript is available on \emph{bioRxiv} at \url{https://doi.org/10.1101/2020.10.27.356998} and has been submitted to \href{https://bmcoralhealth.biomedcentral.com/}{\emph{BMC Oral Health}}.
This version of the manuscript \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/compare/f9b3333c625228f4f28211a34f381b9f87c430b0...478f12f982a0804c2c55f1074f2c468764dad512}{has been updated} since the preprint deposition.

This manuscript
(\href{https://habi.github.io/zmk-tooth-cohort-method-manuscript/v/478f12f982a0804c2c55f1074f2c468764dad512/}{permalink})
was automatically generated
from \href{https://github.com/habi/zmk-tooth-cohort-method-manuscript/tree/478f12f982a0804c2c55f1074f2c468764dad512}{habi/zmk-tooth-cohort-method-manuscript@478f12f}
on March 10, 2021.

@@

\leavevmode\hypertarget{ref-10OKzEtEb}{}%
37. Fedlex. \url{https://www.fedlex.admin.ch/eli/cc/2013/617/en}. Accessed 10 Mar 2021.
\end{cslreferences}
